---
title: "Week 2 Assignment"
author: "Zachary Martin"
date: "1/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Developing Data Products - Week 2 Assignment

07 January 2021

##Instructions
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

# Submission
I create an interactive map with a pin and pop up of my home.

## I first clear my global environment and set my working directory
```{r warning=FALSE, error=FALSE}
rm(list=ls())
setwd("/Users/zacharymartin/Desktop/Coursera/DevDataProducts")
```  

```{r, echo=TRUE}
library(leaflet)
my_map <- leaflet() %>%
  addTiles() %>%
addMarkers(lat=32.3402946, lng=-106.7451672, popup = "Home is Where the Heart Is!")

my_map
```

## Rubric

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2. Does the web page feature an interactive map that appears to have been created with Leaflet?





