---
title: "Week 3 Assignment"
author: "Zachary Martin"
date: "1/15/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown 

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

## Rubric

- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
- Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## DATA

```{r, echo=FALSE}
data("mtcars")

head(mtcars)
```
## MTCARS Horse Power vs. Mileage Plot

Using the `mtcars` dataset we plot can attempt to understand the factors that lead to better fuel effeciancy.

We plot horse power (`hp`) vs. mileage (`mpg`) spatially along the x/y axes. 

## MTCARS Fuel Effeciancy

```{r, echo=FALSE, fig.align='center', fig.cap='MTCARS FIGURE'}
plot(mtcars$hp, mtcars$mpg, xlab="Horse Power", ylab = "MPG")
```
```{r, echo=FALSE, fig.align='center', fig.cap='MTCARS FIGURE'}
plot_ly(mtcars, x = ~hp, y = ~cyl, 
        type = "scatter", mode = "markers", color = ~mpg)
```
